RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-10-31 doc/paper.tex
plots updated

When one concern of the runtime analysis of the \textsc{Rils}--\textsc{Rols} algorithm on the \textsc{Random} benchmark set, the results are shown by Figure~\ref{fig:runtime_rils_rols}. The following conclusions may be drawn from there.

\begin{itemize}
	\item abc...\fxnote{TODO}
\end{itemize}

>>>>

When one concerns of runtime analysis of the \textsc{Rils}--\textsc{Rols} algorithm on the \textsc{Random} benchmark set w.r.t\ number of variables, the results are shown in Figure~\ref{fig:runtime_rils_rols}. The instances are grouped w.r.t.\ number of variables included into corresponding exact model. The following conclusions may be drawn from there.

\begin{itemize}
	\item As expected, average runtime is getting increased with the increase of the number of variables. 
	\item Note that the average runtime in case of the instances whose exact models have the largest number of variables (5) is about 200s.
	\item The two above-mentioned points indicate efficacy of our method especially in case of expected exact models of a smaller size on the data with small--to--middle levels of noise. In these cases, the algorithm is still able to deliver the reasonable exact percentages, which are larger than 50\%. Note that 
	the models with these characteristics are desirable in the areas of natural sciences due to their interpret-ability more than models represented by complex expressions.   
\end{itemize}
